### 2017-12-11 submission/supplemental.Rmd
add table s3

**Table S1: ANOVA Results of HiFi Taq Differences in Fecal Samples**

@@

**Table S2: Tukey Post-Hoc Results of Significant HiFi Taq Differences in Fecal Samples**

@@

**Table S3: **

@@

>>>>

**Table S1: ANOVA Results of Number of OTUs Differences between HiFi Taq in Fecal Samples**

@@

**Table S2: Tukey Post-Hoc Results of Number of OTUs Differences between HiFi Taq in Fecal Samples**

@@

**Table S3: ANOVA Results of Number of OTUs Differences between HiFi Taq in Mock Samples**

@@

mock_anova <- as.data.frame(read_csv("../data/process/tables/mock_overall_anova_results.csv")) %>% 
  mutate_at(vars(Sum.Sq:F.value), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  filter(sub_sample_level > 500)

colnames(mock_anova) <- c("DF", "Sum Squares", "Mean Squares", "F value", "P-value", "BH", "Cycle", "Sub-Sample Depth")

kable(mock_anova, format = "markdown", align = 'c', padding = 2)
```
